\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-30 Papers/ViscousInstabilities/article_figure1.tex
Updates in Section 4.3

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n.pdf}}
\caption{This is a graphical representation of two different element types. Element A is the \PN[1]{2}, while element B is the \PN[1]{1}. Porosity $\phi_{i}$ and permeability $K_{i}$ are CV-wise quantities, whereas velocity and pressure are primarily represented in FE space. Scalar fields (such saturation, density, viscosity etc) are also represented in CV space.}
\label{fig:fem_elem}
\end{figure}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n.pdf}}
\caption{This is a graphical representation of two different element types. Triangle {\it A} is a representation of the \PN[1]{2} element-pair, whereas triangle {\it B} represents the \PN[1]{1} element-pair. Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are primarily represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.\red{(AS MENTIONED IN PREVIOUS VERSIONS ... THIS IS STILL NOT RIGHT ... IN TRIANG A, MID-LINE CIRCLES ARE BLUE AS THEY ARE PRESSURE NODES!!)}
\label{fig:fem_elem}
\end{figure}
\clearpage
